
#Reproducible Research-PA1
##author: Thomax Young
##date: Wednesday, March 11, 2015


##Loading and preprocessing the data

###1.Load the data 
Make sure that activity.csv and PA1_template.Rmd in the same directory.
Read in the data and take a look at it.

```{r}

act_data<-read.csv("activity.csv")
str(act_data)

```

##What is mean total number of steps taken per day?

###1.Make a histogram of the total number of steps taken each day


```{r}
daily_steps<-tapply(act_data$steps, act_data$date, sum, na.rm=FALSE)
hist(daily_steps, col="blue")
```

###2.Calculate and report the mean and median total number of steps taken per day


```{r}
mean_step<-round(mean(daily_steps,na.rm=TRUE))
median_step<-median(daily_steps,na.rm=TRUE)
```
The mean and median total number of steps taken per day are `r mean_step ` and `r median_step`

##What is the average daily activity pattern?

###1.Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
plot(as.Date(names(daily_steps)),daily_steps, type="l",xlab="Dates")

abline(a=mean(daily_steps, na.rm=TRUE),b=0, col="blue")

```

*you may notic that the X axis was labeled in Chinese because of my system language, if you reKnit this Rmarkdown file, you will get the label of your system language.


###2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
max_steps_interval<-tapply(act_data$steps, act_data$date, which.max)

floor(as.numeric(max_steps_interval)/12)*100+as.numeric(max_steps_interval)%%12*5-5
#With this poor readbility code, the 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps could be calculated

intervals_max<-round(mean(floor(as.numeric(max_steps_interval)/12)*100,na.rm=TRUE))+round(mean(as.numeric(max_steps_interval)%%12,na.rm=TRUE))*5-5


#since the number system of interval counting is 55 system, mean() is not approprate
print(intervals_max)

```
the average 1185th interval across all the days in the dataset contains the maximum number of steps 



##Imputing missing values

###1.Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
sum(is.na(act_data))

```
This is th total number of missing values.



###2.Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. 

Since the median is more robust, NAs were be replaced by median of all interval steps which is 0.


###3.Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r}

act_data_NAfilled<-act_data
act_data_NAfilled$steps[is.na(act_data_NAfilled$steps)]<-0
head(act_data_NAfilled)

```


###4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r}

daily_steps_NAfilled<-tapply(act_data_NAfilled$steps, act_data_NAfilled$date, sum, na.rm=FALSE)
hist(daily_steps, col="red")

#The mean and median with NA removed
print(mean(daily_steps,na.rm=TRUE))
print(median(daily_steps,na.rm=TRUE))
#The mean and median with NA filled with 0
print(mean(daily_steps_NAfilled,na.rm=TRUE))
print(median(daily_steps_NAfilled,na.rm=TRUE))
```

Both mean and median droped since NAs were set 0.



##Are there differences in activity patterns between weekdays and weekends?


###1.Create a new factor variable in the dataset with two levels -- "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.

```{r}
week<-weekdays(as.Date(act_data$date),abbreviate = TRUE)
week[week=="ÖÜÈÕ" | week=="ÖÜÁù"]<-"weekend"
week[week!="weekend"]<-"weekday"
week<-as.factor(week)

##Here is something not reproducible that ,in system using Chinese charictars, R ##automaticly use Chinese as weekday lable. 
```


###2.Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).

```{r}
#Make sure the lattice package has been installed
library(lattice)
act_data_NAfilled<-cbind(act_data_NAfilled,week)

xyplot(steps~interval | week, data=act_data_NAfilled, layout=c(1,2), type="l")
```
